Analysis paper

### 2021-05-24 analysis/analysis.Rmd
save plot
update plot
fix transparency in plot

truth_and_obs_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 1,
                 position = position_dodge(width = 6)) + 
  labs(y = "value", x = "date") + 
  geom_point(aes(shape = classification)) + 
  geom_line() + 
  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
                xmax = max(forecast_dates$christmas) + 14,
                ymin = -Inf,
                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

truth_vs_forecast_2_deaths <- df %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_obs_plot()  + 
  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf), fill = "lightgrey", alpha = 0.002)

@@

scores_over_time_plot <- function(scores) {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = scaled_rel_skill)) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date") + 
  geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
                xmax = max(forecast_dates$christmas) + 14,
                ymin = 0,
                ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

rel_skill_time_2_deaths <- scores_target_forecastdate %>%
  dplyr::filter(target_type == "death") %>%
  scores_over_time_plot() + 
  scale_color_brewer(palette = "Accent") + 
  geom_rect(aes(xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf), fill = "lightgrey", alpha = 0.002)

@@

@@

for (tar in targets) {
  table_dfs[[tar]] <- tbl[target_phase == tar, 
                          .("Model" = model, 
                            # "Target" = target_phase,
                            "WIS" = interval_score,
                            # "Rel. skill" = scaled_rel_skill, 
                            "Sharpn." = sharpness, 
                            "Underp.." = underprediction, 
                            "Overp." = overprediction)#, 
                            # "Bias" = bias,
                            # "50%-Cov." = `50`, 
                            # "90%-Cov." = `90`)
                          ]
  table_dfs[[tar]] <- table_dfs[[tar]][, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]
}

@@

print(pl)
ggsave("plots/distribution_scores.png")

@@

print(tbl_plt)
ggsave("plots/distribution_scores_table.png")

>>>>

truth_and_obs_plot <- function(df) {
  p <- df %>%
  ggplot(aes(y = true_value, x = target_end_date)) + 
  geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                 size = 1.5,
                 alpha = 1,
                 position = position_dodge(width = 6)) + 
  labs(y = "value", x = "date") + 
  geom_point(aes(shape = classification)) + 
  geom_line() + 
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14, # 2wk ahead forecast
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = -Inf,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  theme_light() + 
  facet_wrap(~ location_target, scales = "free", ncol = 2) + 
  theme(legend.position = "bottom") + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

truth_vs_forecast_2_deaths <- df %>%
  dplyr::filter(target_type == "death") %>%
  truth_and_obs_plot()  + 
  scale_color_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1)

@@

scores_over_time_plot <- function(scores) {
  p <- scores %>%
  ggplot(aes(x = as.Date(target_end_date), y = scaled_rel_skill)) + 
  geom_line(aes(colour = model)) + 
  geom_point(aes(shape = classification, colour = model)) + 
  theme_light() + 
  facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
  theme(legend.position = "bottom") +
  labs(y = "relative skill", x = "date") + 
  # geom_rect(aes(xmin = min(forecast_dates$christmas) + 14,
  #               xmax = max(forecast_dates$christmas) + 14,
  #               ymin = 0,
  #               ymax = Inf), fill = "lightgrey", alpha = 0.002) +
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_y_log10() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                          max(forecast_dates$full_hub_period)))
  return(p)
}

@@

rel_skill_time_2_deaths <- scores_target_forecastdate %>%
  dplyr::filter(target_type == "death") %>%
  scores_over_time_plot() + 
  scale_color_brewer(palette = "Accent") + 
  annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
                xmax = max(forecast_dates$death_not_scored) + 14,
                ymin = 0,
                ymax = Inf, fill = "grey10", alpha = 0.1)

@@

 tbl <- tbl[, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]

@@

for (tar in targets) {
  table_dfs[[tar]] <- tbl[target_phase == tar, 
                          .("Model" = model, 
                            # "Target" = target_phase,
                            "WIS" = interval_score,
                            # "Rel. skill" = scaled_rel_skill, 
                            "Sharpn." = sharpness, 
                            "Underp.." = underprediction, 
                            "Overp." = overprediction)#, 
                            # "Bias" = bias,
                            # "50%-Cov." = `50`, 
                            # "90%-Cov." = `90`)
                          ]
}

@@

pl
ggsave("plots/distribution_scores.png")

@@

tbl_plt <- ggplotify::as.ggplot(tbl_plt)

tbl_plt

ggsave("plots/distribution_scores_table.png")

tbl[, 
    .("Model" = model, 
      "Target" = target_phase,
      "WIS" = interval_score,
      # "Rel. skill" = scaled_rel_skill, 
      "Sharpn." = sharpness, 
      "Underp.." = underprediction, 
      "Overp." = overprediction)#, 
    # "Bias" = bias,
    # "50%-Cov." = `50`, 
    # "90%-Cov." = `90`)
] %>%
  gt(rowname_col = "Model", 
     groupname_col = "Target")
